Appendix for 'Framing Effects in the Wild

### 2022-08-24 paper/appendix.Rmd
Drop unnecessary parts

```{r inselection fig.cap = "Coefficients of OLS regression of readership on migration attitude across waves. Vertical lines indicate 95% confidence intervals, dashed (red) vertical line indicates editorial change."}

@@

*Transformed to [-3, 3].*

@@

#### Treatment groups across time, by prior attitude

```{r did_imm_att_plot_groups}

fread(here('data/raw/gles/Panel/long_cleaned.csv')) %>% 
  filter(init_mig_groups != "", !is.na(`1130_clean`), !is.na(treat)) %>% 
  group_by(init_mig_groups, treat, wave) %>% 
  summarise(
    date_clean = min(date_clean, na.rm = T),
    `1130_clean` = mean(`1130_clean`, na.rm = T)
  ) %>% 
  ggplot(aes(x = date_clean, y = `1130_clean`, lty = !treat, col = init_mig_groups)) +
  geom_line() +
  geom_vline(xintercept = as.Date("2017-02-01"), lty = 2, col = "red") + 
  # facet_wrap(~init_mig_groups, ncol = 1) + 
  theme_minimal()

#### Effect by prior opinion

```{r linearEffect}

InterLinear() + 
  InterLinear(placebo = T)

#### Regression to the mean among Bild readers

-   Placebo-treatment post Bundestagswahl (3-6 months after treatment)
-   Exclusing Bild readers actually treated

```{r}
DiDPlot(placebo = T, exclude_pretreated = T, legend_position = "None") + InterLinear(placebo = T, exclude_pretreated = T)
```

@@

DiDModels(dv_name = "1130_clean", 
          ctrl_var  = "cond",
          ctrl_name = "Initial Migration Att.")

#### Number of respondents in each group

```{r treat_initmig_n, fig.cap="Number of respondents in treatment and control group by pre-existing attitude."}

gles_p_long <- 
  fread(here('data/raw/gles/Panel/long_cleaned.csv')) %>% 
  filter(wave == "1")

table(gles_p_long$init_mig, gles_p_long$treat) %>% 
  knitr::kable()

rm(gles_p_long)

#### Number of observations

```{r treat_initmig_obs, fig.cap="Number of observations in treatment and control group by pre-existing attitude."}

table(gles_p_long$init_mig, gles_p_long$treat) %>% 
  knitr::kable()

rm(gles_p_long)

#### Conservative Outlets only

```{r did_imm_att_cons}

DiDModels("1130_clean", restrict_sample = "conservative_outlets")

```{r did_imm_att_cons_vis}

fread(here('data/raw/gles/Panel/long_cleaned.csv')) %>% 
  filter(init_mig_groups != "", !is.na(`1130_clean`), !is.na(treat)) %>% 
  filter(bild_init | faz_init | welt_init) %>% 
  group_by(init_mig_groups, treat, wave) %>% 
  summarise(
    date_clean = min(date_clean, na.rm = T),
    `1130_clean` = mean(`1130_clean`, na.rm = T)
  ) %>% 
  ggplot(aes(x = date_clean, y = `1130_clean`, lty = !treat, col = init_mig_groups)) +
  geom_line() +
  geom_vline(xintercept = as.Date("2017-02-01"), lty = 2, col = "red") + 
  ggtitle("Immigration attitudes among Bild readers across time", "Compared to FAZ & Welt readers") + 
  theme_minimal()

### Outcome: Immigration Attitude Nonresponse (1130 = -99)

```{r did_imm_dodge}

DiDModels("1130_dodge")

@@

DiDModels("1210_clean")

### Outcome: Integration Attitude Nonresponse (1210 = -99)

## General Nonresponse/Attrition (1130 = -95)

```{r did_part}

DiDModels("participation")

@@

### Outcome: Voting AfD (190b)

Bei der Bundestagswahl können Sie ja zwei Stimmen vergeben. Die Erststimme für einen Kandidaten aus Ihrem Wahlkreis und die Zweitstimme für eine Partei. Was werden Sie auf Ihrem Stimmzettel ankreuzen?

```{r afd_vote}

DiDModels("afd_vote")

@@

### Outcome: Voting Nonresponse (190b = -99 \| -98)

```{r vote_mis}

DiDModels("vote_miss")

@@

**Sizable effect, most likely among liberals.**

DiDModels("430i_clean")

**Decrease, if anything. Most sizable among liberals, but disappers when controlling for individual FEs.**

## Variable: Issue Considerations

### Outcome: MIP Migrant Crime (840s)

```{r did_mip_mig_crime}

DiDModels("mip_mig_crime")

No effect, but also very low N.

DiDModels("mip_mig")

**NO effect on general problem perception of migration.**.

### Outcome: Crime Attitude (2880h)

DiDModels("2880h_clean")

*Nothing.*

### Outcome: Correlation of Crime Attitude (2880h) & Immigration Attitude (1130)

#### Question

@@

@@

(cannot show this by subgroup bc would condition on pre-treatment opinion, which restricts variation on migration attitudes to 0, hence no correlation)

@@

## Variable: Accuracy Motivation

**This variable is only measured post-treatment**

### Mean accuracy motivation by initial immigration attitude

```{r acc_mot_means}

gles_p_long %>% 
  filter(!is.na(init_mig)) %>% 
  group_by(init_mig) %>% 
  summarise(acc_mot = mean(`1555d_clean`, na.rm = T)) %>% 
  ggplot(aes( x = init_mig, y = acc_mot)) +
  geom_bar(stat = "identity", fill = "lightblue") +
  xlab("Initial Immigration Opinion") +
  ylab("Accuracy motivation") +
  theme_minimal()

### DiD by post-treatment accuracy motivation

```{r did_acc_mot}

DiDModels("1130_clean",
          cond_var = "acc_goal",
          cond_name = "Accuracy Motivation")

# TWFE: BERT Estimates

## Distribution of Independent Variable

```{r bert_dist}

fread(here("data/processed/merged_bert.csv")) %>% 
  ggplot(aes(crime_label_share)) + 
  geom_histogram(bins = 50, col = "white") +
  theme_minimal()

(1) 1 Zuzug von Ausländern erleichtern
(2) 2\
(3) 3\
(4) 4\
(5) 5\
(6) 6\
(7) 7 Zuzug von Ausländern einschränken

```{r ind_imm_att}

TWFEModels("1130_clean")

### Outcome: Immigration Attitude Nonresponse (1130 = -99)

```{r ind_imm_dodge}

TWFEModels("1130_dodge")

```{r ind_int_att}

TWFEModels("1210_clean")

### Outcome: Integration Attitude Nonresponse (1210 = -99)

```{r ind_int_dodge}

TWFEModels("1210_dodge")

## Conditioning on Prior Exposure

### DV: Immigration Attitude

```{r ind_cond_exp_lag}

TWFEModels("1130_clean", 
           cond = "crime_label_share_lag", 
           cond_name = "\nLagged Exposure")

Exposure has no conditioning effect - maybe conditional effect IS ceiling effect? (but still holds compared to conservative news consumers?)

### Outcome: Voting AfD (190b)

Bei der Bundestagswahl können Sie ja zwei Stimmen vergeben. Die Erststimme für einen Kandidaten aus Ihrem Wahlkreis und die Zweitstimme für eine Partei. Was werden Sie auf Ihrem Stimmzettel ankreuzen?

### Outcome: Voting Nonresponse (190b = -99 \| -98)

```{r ind_afd_dodge}

TWFEModels("vote_miss")

```{r ind_afd_vote}

TWFEModels("430i_clean")

## Variable: Issue Considerations

### Outcome: MIP Migrant Crime (840s)

```{r ind_mip_mig_crime}

TWFEModels("mip_mig_crime")

```{r ind_mip_mig}

TWFEModels("mip_mig")

## TWFE Conditional on Paper Consumed (driven by Bild-readers?)

TWFEModels("1130_clean", cond_var = "bild_init", cond_name = "Paper: Bild")

Effect **lower** among Bild readers!

<!-- # TWFE: STM Estimates -->

<!-- **STM estimates currently NOT reliable - fix 04a_merge_stm.R** -->

<!-- ## Distribution of Independent Variable -->

<!-- ```{r stm_dist} -->

<!-- fread(here("data/processed/merged_stm.csv")) %>%  -->

<!--   ggplot(aes(crime_label_share)) +  -->

<!--   geom_histogram(bins = 50, col = "white") + -->

<!--   theme_minimal() -->

<!-- ``` -->

<!-- ## Variable: Immigration Attitudes -->

<!-- ### Outcome: Reduce Immigration (1130) -->

<!-- Jetzt geht es um Zuzugsmöglichkeiten für Ausländer. Sollten die Zuzugsmöglichkeiten für Ausländer erleichtert oder eingeschränkt werden? -->

<!-- (1) 1 Zuzug von Ausländern erleichtern  -->

<!-- (2) 2   -->

<!-- (3) 3   -->

<!-- (4) 4   -->

<!-- (5) 5   -->

<!-- (6) 6   -->

<!-- (7) 7 Zuzug von Ausländern einschränken -->

<!-- ```{r ind_imm_att_stm} -->

<!-- TWFEModels("1130_clean", dataset = "stm") -->

<!-- ``` -->

<!-- ### Outcome: Immigration Attitude Nonresponse (1130 = -99) -->

<!-- ```{r ind_imm_dodge_stm} -->

<!-- TWFEModels("1130_dodge", dataset = "stm") -->

<!-- ``` -->

<!-- ### Outcome: Integration Attitude (1210) -->

<!-- Es gibt unterschiedliche Auffassungen darüber, wie sehr sich Ausländer in Deutschland anpassen sollten. Manche denken, dass sich Ausländer vollständig an die deutsche Kultur anpassen sollten. Andere denken, Ausländer sollten auch hier möglichst nach der eigenen Kultur leben können.  -->

<!-- (1) Ausländer sollten sich vollständig an die deutsche Kultur anpassen  -->

<!-- (2)   -->

<!-- (3)   -->

<!-- (4)   -->

<!-- (5)   -->

<!-- (6)   -->

<!-- (7) Ausländer sollten möglichst nach eigener Kultur leben können  -->

<!-- ```{r ind_int_att_stm} -->

<!-- TWFEModels("1210_clean", dataset = "stm") -->

<!-- ``` -->

<!-- ### Outcome: Integration Attitude Nonresponse (1210 = -99) -->

<!-- ```{r ind_int_dodge_stm} -->

<!-- TWFEModels("1210_dodge", dataset = "stm") -->

<!-- ``` -->

<!-- ## Conditioning on Prior Exposure -->

<!-- ### DV: Immigration Attitude -->

<!-- ```{r ind_cpond_explag_stm} -->

<!-- TWFEModels("1130_clean",  -->

<!--            cond = "crime_label_share_lag",  -->

<!--            cond_name = "\nLagged Exposure", -->

<!--            dataset = "stm") -->

<!-- ``` -->

<!-- Exposure has no conditioning effect - maybe conditional effect IS ceiling effect? (but still holds compared to conservative news consumers?) -->

<!-- ## Variable: Voting Behaviour -->

<!-- ### Outcome: Voting AfD (190b) -->

<!-- Bei der Bundestagswahl können Sie ja zwei Stimmen vergeben. Die Erststimme für einen Kandidaten aus Ihrem Wahlkreis und die Zweitstimme für eine Partei. Was werden Sie auf Ihrem Stimmzettel ankreuzen?  -->

<!-- ### Outcome: Voting Nonresponse (190b = -99 | -98) -->

<!-- ```{r ind_afd_dodge_stm} -->

<!-- TWFEModels("vote_miss", dataset = "stm") -->

<!-- ``` -->

<!-- ### Outcome: Scalometer AfD (430i) -->

<!-- ```{r ind_afd_scale} -->

<!-- TWFEModels("430i_clean", dataset = "stm") -->

<!-- ``` -->

<!-- ## Variable: Issue Considerations -->

<!-- ### Outcome: MIP Migrant Crime (840s) -->

<!-- ```{r ind_mip_mig_crime_stm} -->

<!-- TWFEModels("mip_mig_crime", dataset = "stm") -->

<!-- ``` -->

<!-- ### Outcome: MIP Migration (840s) -->

<!-- ```{r ind_mip_mig_stm} -->

<!-- TWFEModels("mip_mig", dataset = "stm") -->

<!-- ``` -->

<!-- # TWFE Conditional on Paper Consumed (driven by Bild-readers?) -->

<!-- ```{r ind_cond_paper_stm} -->

<!-- TWFEModels("1130_clean", cond_var = "bild_init", cond_name = "Paper: Bild", dataset = "stm") -->

<!-- ``` -->

>>>>

```{r inselection, fig.cap="Coefficients of OLS regression of readership on migration attitude across waves. Vertical lines indicate 95% confidence intervals, dashed (red) vertical line indicates editorial change."}

@@

@@

@@

SingleDVModel('1130_clean')

@@

SingleDVModel("1210_clean")

@@

#### QUESTION TEXT MISSING

#### DiD Estimate

SingleDVModel("430i_clean")

@@

## Variable: Issue Importance

#### QUESTION TEXT MISSING

#### DiD Estimate

SingleDVModel("mip_mig")

@@

## Variable: Crime Considerations

### Attitudes towards fighting crime (2880h)

@@

#### Direct Effect

SingleDVModel("2880h_clean")

@@

@@
